Manuscript draft

### 2019-09-11 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

[**NOBBY, please pay special attention to this paragraph**]. We show that FACF are broadly consistent in their responses to climate drivers on the global scale (with the exception of some differences in MAT-MAP interactions; Fig. 4), with no major trends in C allocation among the variable pairs tested (Fig. 2; **Some SI table**). Although variation in allocation has been observed along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]--along with non-climatic axes of stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], and forest structure [@taylor_greater_2019]--variation in relation to climate is not apparent at the global scale within ForC, which contains the bulk of relevant data. Our conclusion, then, is that hypothesized gradients in allocation along global climate gradients cannot currently be supported for mature forests, although data quantity and standardization is currently insufficent to rule out the possibility that such trends exist. Of particular interest and significance are the relationships amongst $GPP$, net primary productivity ($NPP$ and its components, particularly $ANPP_{woody-stem}$), and respiration ($R_{auto}$ and components). There have been suggestions that tropical forests tend to have low carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$), which are based on observations of low $CUE$ in old-growth tropical forests relative to (mostly younger) extratropical forests [@de_lucia_forest_2007; [Malhi 2012](https://www.researchgate.net/publication/227837530_The_productivity_metabolism_and_carbon_cycle_of_tropical_forest_vegetation); @anderson-teixeira_carbon_2016], but our analysis suggests that these low values might more appropriately be attributed to the fact that these forests are old than to their tropical climate. Indeed, $CUE$ is known to decline with forest age ([@de_lucia_forest_2007];**REFS(NOBBY)**) but appears to be roughly independent of $GPP$ [@litton_carbon_2007]. Similarly, it has been suggested that respiration, maintenance costs, and/or allocation to functions other than woody growth increase more rapidly with temperature than does $GPP$ (**REFS**; Larjavaara & Muller-Landau 2011), implying that $NPP$ and $ANPP_{woody-stem}$ would have a shallower slope than $GPP$. There is some indication that this may be the case (Fig. 2), but careful methodological standardization across a consistent set of mature forest sites will be necessary to determine whether any climate-driven gradients in allocation exist at the global scale.

One interesting observation was that climate tends to explain more variation in the major fluxes ($GPP$, $NPP$, $R_{auto}$ - latitude R^2≥48%) than in subsidiary fluxes (latitude R^2<27% for $BNPP_{fine.root}$, $R_{auto-root}$,$ANPP_{woody-stem}$) (Fig. 2; **some SI table?**). There are two non-exclusive potential explanations for this. First, it may be that methodological variation is larger relative to flux magnitude for some of the subsidiary fluxes. Belowground fluxes in particular are difficult to quantify, and measurement methods for the belowground fluxes considered here may be measured through fundamentally different approaches (*e.g.*, minirhizotrons, ingrowth cores, or sequential coring for $BNPP_{root-fine}$; root exclusion, stable isotope tracking, or gas exchange of excised roots for $R_{auto-root}$), and sampling depth is variable and often insufficient to capture the full soil profile. $ANPP_{woody-stem}$, which is also poorly explained by latitude or climate, is more straightforward to measure but is subject to variability introduced by differences such as biomass allometries applied, minimum plant size sampled, and exclusion or inclusion of branch fall (**?- Becky, did we end up lumping? REF**). However, methodological variation and uncertainty affects all of fluxes considered here--not necessarily any less than the aforementioned, and some of the larger fluxes that vary more strongly with respect to climate (ANPP, NPP) are estimated by summing uncertain component fluxes. Second, differences among variables in the proportion of variation explained by climate could indicate that factors other than climate have significant influence over subsidiary fluxes. *This is consistent with the results we find for allocation among fluxes: although climate has a significant influence on subsidiary fluxes, it is not the only factor that is important, and many other local- and regional-scale factors  influence the way carbon is allocated among subsidiary fluxes. We would expect that this would reduce the strength of the effect of climate on subsidiary fluxes.* [**work on this second part, add refs**]

>>>>

[**NOBBY, please pay special attention to this paragraph**]. We show that FACF are broadly consistent in their responses to climate drivers on the global scale (with the exception of some differences in MAT-MAP interactions; Fig. 4), with no major trends in C allocation among the variable pairs tested (Fig. 2; **Some SI table**). Although variation in allocation has been observed along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]--along with non-climatic axes of stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], and forest structure [@taylor_greater_2019]--variation in relation to climate is not apparent at the global scale within ForC, which contains the bulk of relevant data. Our conclusion, then, is that hypothesized gradients in allocation along global climate gradients cannot currently be supported for mature forests, although data quantity and standardization is currently insufficent to rule out the possibility that such trends exist. Of particular interest and significance are the relationships amongst $GPP$, net primary productivity ($NPP$ and its components, particularly $ANPP_{woody-stem}$), and respiration ($R_{auto}$ and components). There have been suggestions that tropical forests tend to have low carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$), which are based on observations of low $CUE$ in old-growth tropical forests relative to (mostly younger) extratropical forests [@de_lucia_forest_2007; [Malhi 2012](https://www.researchgate.net/publication/227837530_The_productivity_metabolism_and_carbon_cycle_of_tropical_forest_vegetation); @anderson-teixeira_carbon_2016], but our analysis suggests that these low values might more appropriately be attributed to the fact that these forests are old than to their tropical climate. Indeed, $CUE$ is known to decline with forest age ([@de_lucia_forest_2007];**REFS(NOBBY)**) but appears to be roughly independent of $GPP$ [@litton_carbon_2007]. Among our sites with relevant data, there is indication in our data that CUE or $ANPP_{woody-stem}$/$GPP$ increase with latitude (**some SI table**). Careful methodological standardization across a consistent set of mature forest sites will be necessary to determine whether any climate-driven gradients in allocation exist at the global scale.

One interesting observation was that climate tends to explain more variation in the major fluxes ($GPP$, $NPP$, $R_{auto}$ - latitude R^2≥48%) than in subsidiary fluxes (latitude R^2<27% for $BNPP_{fine.root}$, $R_{auto-root}$,$ANPP_{woody-stem}$) (Fig. 2; **some SI table?**). There are two non-exclusive potential explanations for this. First, it may be that methodological variation is larger relative to flux magnitude for some of the subsidiary fluxes. Belowground fluxes in particular are difficult to quantify, and measurement methods for the belowground fluxes considered here may be measured through fundamentally different approaches (*e.g.*, minirhizotrons, ingrowth cores, or sequential coring for $BNPP_{root-fine}$; root exclusion, stable isotope tracking, or gas exchange of excised roots for $R_{auto-root}$), and sampling depth is variable and often insufficient to capture the full soil profile. $ANPP_{woody-stem}$, which is also poorly explained by latitude or climate, is more straightforward to measure but is subject to variability introduced by differences such as biomass allometries applied, minimum plant size sampled, and exclusion or inclusion of branch fall (**?- Becky, did we end up lumping? REF**). However, methodological variation and uncertainty affect all of fluxes considered here--not necessarily any less than the aforementioned, and some of the larger fluxes that vary more strongly with respect to climate ($ANPP$, $NPP$) are estimated by summing uncertain component fluxes. Second, differences among variables in the proportion of variation explained by climate may be attributable to more dicrect climatic control over $GPP$ than subsidiary fluxes. That is, subsidiary fluxes may be shaped by climate both indirectly through its influence on $GPP$ and potentially respiration and directly through any climatic influence on C allocation, as well as by many other local- and regional-scale factors (**REFS**).
